A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-10 paper/draft.tex
add employment spells

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_median_wage.pdf}
    \caption{\textbf{Wage Gap between Partisans and Non-Partisans}. The graph tracks the time trend in the median wage }
    \label{fig:wage_differential}
\end{figure}

Additionally

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_median_wage.pdf}
    \caption{\textbf{Wage Gap between Partisans and Non-Partisans}. The graph tracks the time trend in the median wage of employees prior to entering the municipal bureaucracy.}
    \label{fig:wage_differential}
\end{figure}

Additionally, these same workers tend to have a longer experience working in the formal sector prior to employment. Combined with the higher compensations, the employment evidence suggests that that party members who first enter the bureaucracy in the initial years of the mandate belong to a wealthier strata than their non-partisan counterparts.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_work_experience_mean.pdf}
    \caption{\textbf{Work Experience Differential between Partisans and Non-Partisans}. Partisan bureaucrats tend to arrive from longer work tenures in the non-municipal sectors.}
    \label{fig:work_experience}
\end{figure}
